---
  title: "Where Do People Drink The Most Beer, Wine And Spirits? "
  output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
  pdf_document:
    toc: yes
---

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)    # scrape websites
library(purrr)  
library(lubridate) #to handle dates
```


```{r, load_alcohol_data}
library(fivethirtyeight)
data(drinks)


# or download directly
# alcohol_direct <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv")

```


What are the variable types? Any missing values we should worry about? 

```{r glimpse_skim_data}
# YOUR CODE GOES HERE
glimpse(drinks)
skim(drinks)

# There are no missing variables
```


Make a plot that shows the top 25 beer consuming countries

```{r beer_plot}
# YOUR CODE GOES HERE


beer_plot <- drinks %>%
  select(beer_servings,country) %>%
  arrange(desc(beer_servings)) %>%
  head(25)
glimpse(beer_plot)

p <- ggplot(beer_plot, aes (x=beer_servings, y=reorder(country, beer_servings), size=1)) + 
  geom_col() + 
   labs(title = "What countries drink the most beers?",
       subtitle = "Top 25 countries world's biggest beer drinkers",
  x = " Beer servings",
  y = " Country") + 
  theme(text=element_text(color="#ABABAB", family='Helvetica'), 
         plot.title  = element_text (size=13, colour="#0000FF"), plot.subtitle = element_text(size=9),
        axis.title =  element_text(size=10, colour="#002144"), axis.title.y= element_text(size=10, colour="#002144"))
p
```


Make a plot that shows the top 25 wine consuming countries

```{r wine_plot}

# YOUR CODE GOES HERE
wine_plot <- drinks %>%
  select(wine_servings,country) %>%
  arrange(desc(wine_servings)) %>%
  head(25)
glimpse(wine_plot)

plot2 <- ggplot(wine_plot, aes (x=wine_servings, y=reorder(country, wine_servings), size=1)) + geom_col()+
    labs(title = "What countries drink the most wine?",
       subtitle = "Top 25 countries world's biggest wine drinkers",
  x = " Wine servings",
  y = " Country") + 
  theme(text=element_text(color="#ABABAB", family='Helvetica'), 
         plot.title  = element_text (size=13, colour="#0000FF"), plot.subtitle = element_text(size=9),
        axis.title =  element_text(size=10, colour="#002144"), axis.title.y= element_text(size=10, colour="#002144"))
plot2
```

Finally, make a plot that shows the top 25 spirit consuming countries
```{r spirit_plot}
# YOUR CODE GOES HERE
spirit_plot <- drinks %>%
  select(spirit_servings,country) %>%
  arrange(desc(spirit_servings)) %>%
  head(25)
glimpse(spirit_plot)

plot3 <- ggplot(spirit_plot, aes (x=spirit_servings, y=reorder(country, spirit_servings) , size=1)) + geom_col() +
    labs(title = "What countries drink the most spirit?",
       subtitle = "Top 25 countries world's biggest spirit drinkers",
  x = " Spirit servings",
  y = " Country") + 
  theme(text=element_text(color="#ABABAB", family='Helvetica'), 
         plot.title  = element_text (size=13, colour="#0000FF"), plot.subtitle = element_text(size=9),
        axis.title =  element_text(size=10, colour="#002144"), axis.title.y= element_text(size=10, colour="#002144"))
plot3
```

What can you infer from these plots? Don't just explain what's in the graph, but speculate or tell a short story (1-2 paragraphs max).

#While each country has its own national drinks, the consumption of beers, wines and spirits is global. Surprinsingly, spirits are the most consumed drinks - above beers and wines. While France leads its peer group (wine category), United Kindgom is not even in the top 10 (beer category). Despite the general assumption that the UK is the leading nation for beer consumption, data here shows the opposite.

